Biden More Favorable Among Female, Black, Asian, Hispanic, Middle Eastern, and Non-gun Owning Voters in the 2020 US Presidential Election

### 2024-03-17 paper/paper.qmd
Fixed minor grammatical errors for final submission

---
title: "Biden More Favorable Among Female, Black, Asian, Hispanic, Middle Eastern, and Non-gun Owning Voters in the 2020 US Presidential Election"
author: 
  - Tam Ly
  - Renfrew Ao-Ieong
  - Rahma Binth Mohammad
thanks: "Code and data are available at: [https://github.com/atn-ly/political_support_in_the_us](https://github.com/atn-ly/political_support_in_the_us)"
date: 16 March 2024
date-format: long
abstract: "The outcome of the 2020 US Presidential Election served as a reflection of the beliefs and attitudes held by Americans. Using data obtained during the fall of 2020 from the Cooperative Election Study, we investigated if a person is likely to vote for Biden, based only on knowing their gender, race, and gun ownership status. The results of our analysis using a Bayesian logistic regression model show that female, Black, Asian, Hispanic, Middle Eastern, and non-gun owning individuals are more likely to support Biden. Our discovery highlights the importance of women’s issues, racial justice, and gun policy on American voters."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

We will now discuss how the variables, `gender`, `race`, and `gunown`, were measured and how they became an entry in our dataset. Each variable was associated with a related question, and the self-reported response of each individual from the online questionnaire was recorded in the dataset. Some notes on measurement error and missing data are required for each variable.

@@

Given that Biden and Trump are far apart on women’s issues, racial justice, and gun policy, we  chose “gender”, “race”, and “gunown” to be the predictor variables in our model. First, since we are interested in forecasting who a respondent is likely to vote for, we used “gender” instead of “gender_post” because it is representative of all adult Americans registered to vote rather than only adult Americans who voted. Second, we used “race” instead of variables by country or region to affirm that race is a social construct with no biological foundation. Third, we used “gunown” instead of variables about gun control because it captures broader opinions rather than specific policy proposals. After exploring the data in the previous section, we found differences in political preference based on these features and that it would be of interest to investigate further.

@@

# Additional data details

>>>>

---
title: "Biden More Favorable Among Female, Black, Asian, Hispanic, Middle Eastern, and Non-gun Owning Voters in the 2020 US Presidential Election"
author: 
  - Tam Ly
  - Renfrew Ao-Ieong
  - Rahma Binth Mohammad
thanks: "Code and data are available at: [https://github.com/atn-ly/political_support_in_the_us](https://github.com/atn-ly/political_support_in_the_us)"
date: 16 March 2024
date-format: long
abstract: "The outcome of the 2020 US Presidential Election served as a reflection of the beliefs and attitudes held by Americans. Using data obtained during the fall of 2020 from the Cooperative Election Study, we investigated if a person is likely to vote for Biden, based only on knowing their gender, race, and gun ownership status. The results of our analysis, using a Bayesian logistic regression model, show that female, Black, Asian, Hispanic, Middle Eastern, and non-gun owning individuals are more likely to support Biden. Our discovery highlights the importance of women’s issues, racial justice, and gun policy on American voters."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

We will now discuss how the variables `gender`, `race`, and `gunown` were measured and how they became an entry in our dataset. Each variable was associated with a related question, and the self-reported responses of each individual from the online questionnaire were recorded in the dataset. Some notes on measurement error and missing data are required for each variable.

@@

Given that Biden and Trump are far apart on women’s issues, racial justice, and gun policy, we  chose `gender`, `race`, and `gunown` to be the predictor variables in our model. First, since we are interested in forecasting who a respondent is likely to vote for, we used “gender” instead of “gender_post” because it is representative of all adult Americans registered to vote rather than only adult Americans who voted. Second, we used “race” instead of variables by country or region to affirm that race is a social construct with no biological foundation. Third, we used “gunown” instead of variables about gun control because it captures broader opinions rather than specific policy proposals. After exploring the data in the previous section, we found differences in political preference based on these features and that it would be of interest to investigate further.

@@
